A New Metric for the Analysis of Swarms using Potential Fields

### 2018-08-21 paper.tex
Minor

Many metrics exist for the analysis of swarms. These metrics can be categorised as \textit{Centroidal-based}, \textit{Agent/Inter-agent distance-based} and \textit{vector-based}. The common denominator of \textit{centroidal} and \textit{Agent/inter-agent distance} metrics are that they \textit{measure} the agent distribution within a swarm based upon distances. \textit{Vector-based} metrics analysis a swarm based upon inter-agent interaction.

@@

\section{Conclusion}\label{Section:MagnitudeDistanceComparison}
%% The two metrics (distance and \textit{cohesion/repulsion}) both measure the structure of a swarm in terms of the distribution of the agents and deviations from a mean. The \textit{cohesion/repulsion} metric also allows the state of the swarm to be identified.
%% 
%% The distance metric is based upon the physical \textit{distribution} of the agents and the cohesion/repulsion metric is based upon the logical \textit{interaction} of the agents.
The distance-based metric measures swarm structure in terms of position of agents. It provides an analysis at a point in time but does not allow the identification of the future behaviour of a swarm as `expanding', `stable' or `contracting'.

@@

The \textit{cohesion/repulsion} metric provides an indication of a swarm's potential future movement. This is independent of the physical distribution of the agents within the swarm.

>>>>

Many metrics exist for the analysis of swarms. These metrics can be categorised as \textit{Centroidal-based}, \textit{Agent/Inter-agent distance-based} and \textit{Magnitude-based}. The common denominator of \textit{centroidal} and \textit{Agent/inter-agent distance} metrics are that they \textit{measure} the agent distribution within a swarm based upon distances. \textit{Magnitude-based} metrics analysis a swarm based upon inter-agent interaction.

@@

\section{Conclusion}\label{Section:MagnitudeDistanceComparison}
%% The two metrics (distance and \textit{cohesion/repulsion}) both measure the structure of a swarm in terms of the distribution of the agents and deviations from a mean. The \textit{cohesion/repulsion} metric also allows the state of the swarm to be identified.
%% 
%% The distance metric is based upon the physical \textit{distribution} of the agents and the cohesion/repulsion metric is based upon the logical \textit{interaction} of the agents.
Distance-based metrics measure a swarm's structure in terms of the position of agents. This is independent of the algorithm that produces the swarm's structure. It provides an analysis at a point in time but does not allow the identification of the future behaviour of a swarm as `expanding', `stable' or `contracting'.

@@

The \textit{cohesion/repulsion} metric is based upon the algorithms that have produced the structure and is therefore an analysis of how the algorithms are performing rather than the structure presented. The new metric also provides an indication of a swarm's potential future movement. This is independent of the physical distribution of the agents within the swarm. The metric also provides the same information as the distance metric in terms of agent distribution when the field effects are consistent across all agents i.e. monolithic field effects. This is shown in Fig. \ref{emerge:FIELDFILL-MAG} and \ref{emerge:FIELDFILL-DIST} by the profiles of the two graphs being the same.
